Truthfulness Verification System

### 2011-02-23 trunk/proposal/paper.tex
changed title
Added the diffs

\subsection{Application of Machine learning algorithms}: 
Though application of machine learning algorithms like using Naive Bayesian,
neural network

\section{2.1 Supervised - Use a naive bayesian classifier}
\section{Unsupervised methods - clustering or Probabilistic LSI}
\section{Partially Supervised methods}

>>>>

\subsection{Application of Machine learning algorithms}: 
Though application of machine learning algorithms like using Naive Bayesian,
neural network etc to build classifiers on the property, value pairs appear
exciting, we are skeptical about their performance primarily due to the variety
of doubtful sentences that may arise. However, we may consider
applying PU-learning on the system which is a technique useful specially when
the training data is small in size. Another closely related technique we wish to
explore is using probabilistic latent semantic indexing.
